\documentclass[10pt]{article}

\usepackage{times}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}

\setlength\parindent{0pt}


\raggedbottom
\sloppy

\title{TCP\\
\emph{TDTS06}}

\author{David Habrman \\ davha227, 920908-2412\\
Jens Edhammer \\ jened502, 920128-5112 }

\date{\today}

\begin{document}

\maketitle

\newpage
\tableofcontents
\newpage

\section{Introduction}

\section{Practice}
\begin{enumerate}
  \item{What are the first and last packets for the POST request?}
  \subitem{232129013 is first and 232293053 is last. First is a POST request,
    last is a reconstructed POST}
  \item{What is the IP address and the TCP port used by the client
    computer (source) that is transferring the file to gaia.cs.umass.edu?}
  \subitem{IP: 192.168.1.102 Port:1161}
  \item{What is the IP address of gaia.cs.umass.edu? On what port number
    is it sending and receiving TCP segments for this connections?}
  \subitem{IP: 128.119.245.12 Port:80}
  \item{What is the sequence number of the TCP SYN segment that is used
    to initiate the TCP connection between the client computer and
    gaia.cs.umass.edu? What is it in the segment that identifies the
    segment as a SYN segment?}
  \subitem{232129012, it has a header flag (SYN)}
  \item{What is the sequence number of the SYNACK segment
    sent by gaia.cs.umass.edu to the client computer in reply
    to the SYN? What is the value of the ACKnowledgement field
    in the SYNACK segment? How did gaia.cs.umass.edu determine
    that value? What is it in the segment that identifies the segment
    as a SYNACK segment?}
  \subitem{SYNACKseqNr: 883061785 ACK:232129013, SYNseqNr+1=ACK. Header flags
    (SYN and ACK). ACK:s everything up to but not including ACK number}
  \item{What is the sequence number of the TCP segment
    containing the HTTP POST command?}
  \subitem{232129013}
  \item{Consider the TCP segment containing the HTTP POST as the first segment
  in the TCP connection. What are the sequence numbers of the first six
  segments in the TCP connection (including the segment containing the
  HTTP POST)? At what time was each segment sent? When was the ACK for each
  segment received? Given the difference between when each TCP segment was
  sent, and when its acknowledgement was received, what is the RTT value for
  each of the six segments? What is the EstimatedRTT value (see page 277 in
  text) after the receipt of each ACK? Assume that the value of the
  EstimatedRTT is equal to the measured RTT for the first segment, and then
  is computed using the EstimatedRTT equation on page 277 for all subsequent
  segments.}
  \subitem{232129013,232129578,232131038,232132498,232133958,232135418.
    0.026477, 0.041737, 0.054026, 0.054690, 0.077405, 0.078157.
    0.053937, 0.077294, 0.124085, 0.169118, 0.217299, 0.267802.
    0.02746, 0.035557, 0.070059, 0.114428, 0.139894, 0.189645.
    0.02746, 0.028472, 0.033670, 0.043765, 0.055781, 0.072514.}
  \item{What is the length of each of the first six TCP segments?}
  \subitem{first is 565 bytes, all others are 1460 bytes}
  \item{What is the minimum amount of available buffer space advertised at
    the receiver for the entire trace? Does the lack of receiver buffer space
    ever throttle the sender?}
  \subitem{5840 form the SYNACK. It does not throttle the sender, we send much
    smaller packets (1460).}
  \item{Are there any retransmitted segments in the trace file? What did you
    check for (in the trace) in order to answer this question?}
  \subitem{No, we checked for tcp segments with the same sequence number as
    an earlier packet.}
  \item{How much data does the receiver typically acknowledge in an ACK?
    Can you identify cases where the receiver is ACKing every other
    received segment (see Table 3.2 on page 285 in the text).}
  \subitem{Usually it ACK:s only one segment (1460 bytes) but later on
    it ACK:s every other segment e.g. packet 105.}
  \item{What is the throughput (bytes transferred per unit time)
    for the TCP connection? Explain how you calculated this value.}
  \subitem{Total data: 150 KB, and the last ACK comes in at 5.651141 including
    the handshake. This gives a throughput of 150*8/5.651141 = 212.3 KBit/s.}
\end{enumerate}

\section{Task A} \subsection{High Level} At high level a simple (SYN,SYNACK,ACK)
handshake is performed. The data is sent in smaller packets (1460 bytes), and
every so often (every 6 packets) the data gets the PSH flag which sends the
partial data up to the application layer. The last packet in each cycle is a
rest packet and migh contain less data than 1460 bytes. All the six packets need
to be ACK:ed before sending 6 new packets. When all tcp-packets have been ACK:ed
the transmission is complete. \subsection{Low Level} Initially all packets are
ACK:ed indiviually, after a while the connection is deemed stable enough to
start ACK:ing multiple in order packets using cumulative ACK's. In other words,
the server waits for a longer timeout period for inorder packets and ACK's
multiple packets with a single ACK. This is connected to the estimation of the
RTT.Packet losses are handled by simply resending the packets. To detect
packetlosses TCP uses several small and quite intelligent methods. The ACK sent
on a packet ACK's all data that have been recieved in order so far. So we
quickly discover if we send packet 12 and packet 10 hasn't been recieved and we
can resend it. A lost ACK is solved by cumulative ACK's so a later ACK can ACK
all previous packets.

\section{Task B}
\begin{enumerate}
  \setcounter{enumi}{12}
  \item{Use the Time-Sequence-Graph (Stevens) plotting tool to view the sequence
  number versus time plot of segments being sent from the client to the server
  (Figure 2a and Figure 2b). For each of the two traces, can you identify where
  TCP's slow start phase begins and ends, and where congestion avoidance takes
  over? If you can, explain how. If not, explain why not. To better identify these
  phases, you may need to find the number of unacknowledged packets (or bytes) at
  different times and plot the unacknowledged packets (y-axis) as a function of
  time (x-axis). Note that the number of unacknowledged packets at different times
  can be found by comparing the number of packets that have been sent with the
  number of packets that have been acknowledged. After plotting the number of
  unacknowledged packets versus time, comment on ways in which the measured data
  differs from the idealized behavior of TCP that we've studied in the text.}

  \subitem{The slowstart phase starts immediately in a (packet 4) and ends after a
  few packets (packet 13), in b we have some packet loss in the start and it's a
  bit harder to tell where the slow phase ends, but around packet 12 seems
  reasonable. In b we also see congestion control. It takes over at packet 65
  which can be seen by the sequence number divide by time goes linear.}

  \item{Explain the relationship between (i) the congestion window, (ii) the
  receiver advertised window, (iii) the number of unacknowledged bytes, and (iv)
  the effective window at the sender.}
  \subitem{(i) The Congestion window,
  starts out small and increases as long as there is no packet losses. When a
  packet loss is detected the window is cut in half. }
  \subitem{(ii) Advertised
  Reciever Window, is how big of a buffer the reciever has allocated for the
  TCP-packets coming in. We can't send packets exceeding this size without
  acknowledging that they have indeed been recieved (and thus freed from the
  buffer.)}
  \subitem{(iii) The number of unacknowledged bytes, is not allowed to break the
  following equation. $ \textit{\#numUnAckBytes} \leq$ min{cwnd, rwnd}}
  \subitem{(iv) The effective sender window in total is the same as the allowed
  unacknowledged bytes. The current available send window must take in account the
  amount of currently unacknowledged bytes in transit.} \item{Is it generally
  possible to find the congestion window size (i.e. cwnd) and how it changes with
  time, from the captured trace files? If so, please explain how. If not, please
  explain when and when not. Motivate your answer and give examples. Your answer
  may also benefit from trying to describe and discuss your answer in the context
  of the two prior questions, for example.}
  \subitem{You can see the congestion
  window if you load the link so heavily that the congestion window starts to take
  effect.}
\end{enumerate}

\section{Task C}
\begin{enumerate}
  \setcounter{enumi}{15}
  \item{}
  \subitem{}
  \item{}
  \subitem{}
  \item{}
  \subitem{}
\end{enumerate}





\section{Discussion}

\end{document}
